---
title: "Lokaverkefni"
author: "Þórgnýr Thoroddsen"
date: "11/23/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggmap)
library(geo)
library(dplyr)
```

```{r}
Length <- read.table("./data/Length.csv", header = TRUE, sep = ",")
Station <- read.table("./data/Station.csv", header = TRUE, sep = ",")
Subsampling <- read.table("./data/Subsampling.csv", header = TRUE, sep = ",")
```


```{r}
names(Station)[1]<-'id'
names(Subsampling)[1]<-'id'
names(Length)[1]<-'id'
```

From the date columns read the year of the survey.

```{r}
Station$year <- format(as.Date(Station$date1, format="%Y-%m-%d"),"%Y")
```

Change lon1/lat1 to lon/lat

```{r}
names(Station)[4] <- "lon"
names(Station)[5] <- "lat"
```

Removing NA values from Station for aestetic purposes.

```{r}
Station.NAfree <- Station[complete.cases(Station), ]
```

Investigate the location of the tow station. Choose a year, e.g. the year 2005, and plot the location of the tows from the stations table on a map of the Icelandic continental shelf. Using geom_segment, illustrate the start and end points of the tows.

Begin by subsetting the data by the year 1998.

```{r}
Station.1998 <- 
  filter(Station.NAfree, year == '1998')
```

Plot the locations of the tows.

```{r}
eff.plot <- 
  ggplot(Station.1998, aes(lon, lat)) +

  ## depth contours (as polygons
  geom_polygon(data = gbdypi.100, alpha = 0.1, col = 'gray90') +
  geom_polygon(data = gbdypi.200, alpha = 0.1, col = 'gray90') + 
  geom_polygon(data = island, col = 'gray90') +

  ## locations
  geom_point(size = 0.1) +

  ## coordinate map (changed from cartesian to mercator)
  coord_map('mercator', xlim = c(-28, -11), ylim = c(62.5, 68)) +
  xlab('Longitude') +
  ylab('Latitude') + 

  ## manual scales
  scale_colour_manual(values = c('red', 'blue', 'green')) +

  ## themes and change the legend position
  theme_bw() +
  theme(panel.border = element_rect(colour = 'black', size = 2),
        legend.position = c(0.9, 0.85),
        legend.background = element_rect(fill = 'white')) +

  ## gridlines
  scale_x_continuous(breaks = seq(-26, -11, 2))  +
  scale_y_continuous(breaks = seq(63, 67, 1)) +

  ## Lines
  geom_segment(aes(x = lon, y = lat, xend = lon2, yend = lat2, colour = "Direction and length of tow"), arrow = arrow(length = unit(0.1, "cm"))) +

  ## Removing legend name and reposition.
  theme(legend.title = element_blank()) +
  theme(legend.position = "right")

eff.plot
```

For each station, calculate the ratio of the total number to measured fish i.e. 
$$r = \frac{n.total}{n.measured}$$
and when $r$ is NA replace it with the value 1.

```{r}
Subsampling$ratio <- 
  Subsampling$n.total/Subsampling$n.measured

Subsampling$ratio[Subsampling$ratio == Inf] <- 1
```





